Clustering of Distributions on 1-Dimensional Manifolds

### 2021-09-01 scratch/distributions-on-1d-manifolds.Rmd
proof sketch for general case

$$P(D_i \leq \delta) = 1 - \int_0^{1-\delta} (i-1) \binom{n}{i-1} f(x) (F(x))^{i-1} (1 - F(x + \delta))^{n-i} dx$$

Under certain conditions (namely $F(x + \delta) \geq F(x) + \delta$), we can make the substitution $u = F(x)$ and have the result

$$P(D_i \leq \delta) \leq 1- \int_0^{1 - \delta} (i-1) \binom{n}{i-1} u^{i-1} (1 - u - \delta)^{n-i} du$$

which gives the same result as in the uniform case.

>>>>

$$P(D_i \leq \delta) = 1 - \int_0^{1-\delta} \frac{n!}{(n-i+1)! (i-2)!} (F(x))^{i-2} (1 - F(x + \delta))^{n-i} f(x) dx$$

Making the approximation $F(x+\delta) \approx F(x) + \delta f(x)$ 
and bounding $f(x) \geq a > 0$, we get:

$$P(D_i \leq \delta) \geq 1 - \int_0^{1-\delta} \frac{n!}{(n-i+1)! (i-2)!} (F(x))^{i-2} (1 - F(x) - a \delta)^{n-i} f(x) dx$$

Then making the substitution $u = F(x) \implies du = f(x) dx$, we get

$$1 - \int_0^{F(1-\delta)} \frac{n!}{(n-i+1)! (i-2)!} u^{i-2} (1 - u - a \delta)^{n-i} du$$

Which becomes $1 - C P(n) e^{-n}$ for some $C > 0$ and $P(n)$ is a polynomial of $n$. This goes to 0 as $n \to \infty$, giving us the result $D_i \stackrel{p}{\to} 0$.

### 2021-09-01 scratch/distributions-on-1d-manifolds.tex
proof sketch for general case

\[P(D_i \leq \delta) = 1 - \int_0^{1-\delta} (i-1) \binom{n}{i-1} f(x) (F(x))^{i-1} (1 - F(x + \delta))^{n-i} dx\]

Under certain conditions (namely \(F(x + \delta) \geq F(x) + \delta\)),
we can make the substitution \(u = F(x)\) and have the result

\[P(D_i \leq \delta) \leq 1- \int_0^{1 - \delta} (i-1) \binom{n}{i-1} u^{i-1} (1 - u - \delta)^{n-i} du\]

which gives the same result as in the uniform case.

>>>>

\[P(D_i \leq \delta) = 1 - \int_0^{1-\delta} \frac{n!}{(n-i+1)! (i-2)!} (F(x))^{i-2} (1 - F(x + \delta))^{n-i} f(x) dx\]

Making the approximation \(F(x+\delta) \approx F(x) + \delta f(x)\) and
bounding \(f(x) \geq a > 0\), we get:

\[P(D_i \leq \delta) \geq 1 - \int_0^{1-\delta} \frac{n!}{(n-i+1)! (i-2)!} (F(x))^{i-2} (1 - F(x) - a \delta)^{n-i} f(x) dx\]

Then making the substitution \(u = F(x) \implies du = f(x) dx\), we get

\[1 - \int_0^{F(1-\delta)} \frac{n!}{(n-i+1)! (i-2)!} u^{i-2} (1 - u - a \delta)^{n-i} du\]

Which becomes \(1 - C P(n) e^{-n}\) for some \(C > 0\) and \(P(n)\) is a
polynomial of \(n\). This goes to 0 as \(n \to \infty\), giving us the
result \(D_i \stackrel{p}{\to} 0\).
